Borel regularity for ODEs and exponential integrals

### 2023-04-24 exp-resurgence.tex
update section proof

\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

\begin{theorem}\label{thm1}
In the previous set-up, for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$: set $\zeta_j=\zeta-\alpha_j$,

\[{\psi}_j(\zeta_j)=\textcolor{magenta}{\zeta_j^{\tau_j-1}}+f_j\] .
\end{theorem}
\textcolor{magenta}{[Paste in statement from {\tt reg-sing-volterra}. Verify the exponent: is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}

@@

\begin{theorem}\label{thm2}
Let $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ be the Laplace transform of $\psi_j$ solutions constructed in Theorem~\ref{thm1}. The following results hold true
\begin{enumerate}
\item $\Psi_j$ is asymptotic to $\series{\Psi}_j$;
\item the Borel sum of $\series{\Psi}_j$ is the same as $\Psi_j$
\end{enumerate}
\end{theorem}

@@

\section{Proof of main results}
\subsection{Borel regularity for ODEs}
\subsection{Borel regularity for thimble integrals}

>>>>

\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
\begin{equation}\label{eqn:standard ODE}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
\end{equation}
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}. Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$. Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully! It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.

@@

\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with

\begin{equation}
\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
\end{theorem}

@@

\begin{theorem}\label{thm2}
For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}

@@

\section{Proof of main results}
\subsection{Borel regularity for ODEs}

\begin{theorem}\label{thm1-dim}
Let $\mathcal{P}$ be a linear differential operator 
\begin{equation}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
\end{equation}

\begin{itemize}
\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
\item $R_0, \ldots, R_d$ are entire functions of exponential type
\end{itemize}

Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and

\begin{equation}
\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
\end{equation}

such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
\end{theorem}
\begin{proof}
It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.  In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$. $Q$ is also a polynomial defined at $\zeta_j=0$. Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$

\begin{align*}
&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
\end{align*}

%In particular, $\Lambda=(-\infty,-2]$.

Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.

\end{proof}

\begin{theorem}\label{thm2-dim}
For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}. Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
\end{theorem}
\begin{proof}
We divide the proof in the following steps:
\begin{itemize}
\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\tilde{\psi}_j:=\mathcal{B}\Psi_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
\item[$(c)$] prove that $\mathcal{L}_{\zeta_j}^{\theta_j}\circ\mathcal{B}\series{\Psi}_j\propto \Psi_j $. 
\end{itemize}
\end{proof}

\subsection{Borel regularity for thimble integrals}
